Predicting instabilities of a tuneable ring laser with an iterative map model

### 2020-11-20 Papers/Journal/Cavity.tex
Apparently this got deleted

% Circulators
\filldraw[fill=white, draw=black] (6,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Optical \\ Circulator};
\draw[->,>=stealth] (6,2.325) arc (90:360:0.325cm);

@@

\filldraw[fill=white, draw=black] (0,4) circle (0.5cm);
\draw[->,>=stealth] (0,4.325) arc (90:360:0.325cm);

>>>>

% Circulators
\filldraw[fill=white, draw=black] (6,2) circle (0.5cm);
\draw[->,>=stealth] (6,2.325) arc (90:360:0.325cm);

@@

\filldraw[fill=white, draw=black] (0,4) circle (0.5cm) node [anchor=south,align=center,yshift=0.5cm] {Optical Circulator};
\draw[->,>=stealth] (0,4.325) arc (90:360:0.325cm);
